Verifying Demonstrations

### 2018-08-22 paper/adversary-model.tex
Improves rationale for witness adversary

\Cref{base-witness-adversary} is the analogous to 
\cref{base-protester-adversary}.
The rationale is the same as for \cref{base-protester-adversary}, the witness 
\(W\) can submit to \(S\) over an anonymous channel, such as \ac{Tor}.
\Cref{fig:witness-adversary} illustrates the roles and relations.

@@

>>>>

\Cref{base-witness-adversary} is the analogous to 
\cref{base-protester-adversary}.
\Cref{fig:witness-adversary} illustrates the roles and relations.

@@

The base rationale is the same as for \cref{base-protester-adversary}, the 
witness \(W\) can submit to \(S\) over an anonymous channel, such as \ac{Tor}.
Anyone who is in the same location will learn that \(W\) was present, we want 
to prevent anyone \emph{not present} to learn that \(W\) was there --- hence we 
do not consider the protester as part of the adversary, only \(S\).
We thus conclude with the strongest adversary against the witness.

\begin{definition}[Strongest witness adversary]
  Things are the same as in \cref{base-witness-adversary}, except that \(S\) 
  learns the witness' identity \(W\).
\end{definition}
